### 2015-10-28 vmcai-2016-tex/approach.tex
Addressed reviewer concerns

\caption{Initializing fields, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
\label{fig:symInit}
\end{figure*}

In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
field $f$, the $\mathrm{min}_l$ function returns
$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
uninitialized locations in $\Lambda$ to make initialization
deterministic.  The set $\rho$ contains reference-location pairs that
represent potential aliases, where $\mathrm{isInit}\lp\rp$ ensures that the references are initialized. 
There are four cases encoded in the
symbolic heap. The first three correspond to the three types of choices made during lazy initialization: (i) $\theta_\mathit{null}$ represents the condition
where $\cfgnt{l}_\mathit{null}$ is possible, (ii)
$\theta_\mathit{new}$ represents the case where $\cfgnt{r}_f$ points
to a fresh location, (iii) each member of $\theta_\mathit{alias}$
restricts $\cfgnt{r}_f$ to a particular alias in $\rho$, and at the
same time, not alias any member of $\rho$ that was initialized earlier
than the current choice.

Unlike the first three cases, which correspond directly to~\gsetxt{} initialization rules, case (iv) is unique to~\symtxt{}. In this case, $\theta_\mathit{orig}$ implements conditional initialization to preserve the original heap structure. This step is necessary in order to maintain homomorphism\footnote{Homomorphism is an important property relied on by the correctness proof.} between symbolic heaps created using~\symtxt{} and the~\gsetxt{} heaps they are intended to represent. 
The sets from each of the four cases are added into the heap on $\cfgnt{r}_f$ after the fields
for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.

@@

\figref{fig:initHeap} illustrates the initialization process. The
graph in~\figref{fig:initHeap}(a) represents the initial heap. The
reference superscripts $s$ and $i$ indicate the partition containing
the reference.  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a
stack reference for the $\cfgt{this}$ variable which has two fields
$x$ and $y$ of the same type. Note that when no constraint is
specified for a location, there is an implicit $\mathit{true}$
constraint. For example, $\cfgnt{r}_0^s$ points to $\cfgnt{l}_0$ on
the constraint $\mathit{true}$. The fields $x$ and $y$ point to the
uninitialized reference $\cfgnt{r}_\mathit{un}$. The graph
in~\figref{fig:initHeap}(b) represents the symbolic heap after the
initialization of the $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$ field
while the graph in~\figref{fig:initHeap}(c) represents the symbolic
heap after the initialization of the
$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$ field following the
initialization of $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$. The list
in~\figref{fig:initHeap}(d) represents the various sets constructed in
the initialization $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$.

@@

Certain rewrite rules depend on auxiliary on the relations in \defref{def:VS} and \defref{def:ST}, such as those in~\figref{fig:fHeap}. There are two rewrite rules in~\figref{fig:fHeap}, one for reading
the value of a field (field-access) and the other for writing to a
field (field-write). Both rules first check that the operations can be
performed on a non-null location. The field-access rewrite rule
in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$ and
uses \figref{fig:symInit}, to get a new symbolic heap that is
initialized on the field $\cfgnt{f}$. The symbolic heap is further
modified to include a new stack reference pointing to the guarded value set
(possible values of the field) returned during the dereferencing; the
new stack reference is the return value from the $\mathbb{VS}$ operation.

@@

Strengthening in the field write creates a value set that contains two
types of locations: those for the case where the write is feasible
(the first call), and those for the case where it is not (the second
call). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
will point to the guarded value set $\cfgnt{L}(\cfgnt{r})$.
Whereas, if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will
continue to point to the constraint location pair it currently
references.  As the references are immutable, the rule creates fresh
references for each $\cfgnt{r}_\mathit{cur}$ and points them to the
appropriate value sets.

@@

The rewrite rule to compare two references in the symbolic heap is
shown in~\figref{fig:eqs}. The equals references-true rewrite rule
returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
\emph{can} be equal. Intutively, $\Phi_\alpha$ contains all
constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may point to
the same location in the symbolic heap. The second set, $\Phi_0$,
contains constraints under which the reference $\cfgnt{r}_0$ points to
corresponding locations such that the reference $\cfgnt{r}_1$
\emph{does not} point to those locations under any
constraint. Finally, the set, $\Phi_1$, contains constraints under
which $\cfgnt{r}_1$ points to corresponding locations and
$\cfgnt{r}_0$ \emph{does not} point to those locations under any
constraint. The three sets of constraints are used to create a new path condition $\phi_g^\prime$
as an update of the current path condition $\phi_g$.  The update is accomplished by first taking the disjunction of the
constraints in $\Phi_\alpha$ to indicate that if any of the
constraints are satisfiable, then references $\cfgnt{r}_0$ and
$\cfgnt{r}_1$ can be equal. This disjunction is then conjoined with $\phi_g$ to form $\phi_g^\prime$. Furthermore, the conjunctions of negations to the
constraints in $\Phi_0$ and $\Phi_1$ is conjoined with $\phi_g^\prime$. This indicates for locations
that are not common to the references, the negations of their
constraints are satisfiable. The rule does not complete (i.e., is not
feasible) if the new global constraint is not satisfied on any
aliasing assignment. In such a case, the $\cfgt{true}$ outcome is not
possible on any symbolic heap. Before the rewrite rule returns
$\cfgt{true}$, it verifies the satisfiability of the updated global heap
constraint. The reference-false is the logical dual of the rule.

>>>>

\caption{Initializing fields, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime$.}
\label{fig:symInit}
\end{figure*}

In~\figref{fig:symInit}, similar to before, given the uninitialized set $\Lambda$ for
field $f$, the $\mathrm{min}_l$ function returns
$(\phi_x\ \cfgnt{l}_x)$ which represents the earliest created uninitialized location in that set.  The set $\rho$ contains reference-location pairs that
represent potential aliases, where $\mathrm{isInit}\lp\rp$ ensures that the references are initialized. 
There are four cases encoded in the
symbolic heap. The first three correspond to the three types of choices made during lazy initialization: (i) $\theta_\mathit{null}$ represents the condition
where $\cfgnt{l}_\mathit{null}$ is possible, (ii)
$\theta_\mathit{new}$ represents the case where $\cfgnt{r}_f$ points
to a fresh location, (iii) each member of $\theta_\mathit{alias}$
restricts $\cfgnt{r}_f$ to a particular alias in $\rho$, and at the
same time, not alias any member of $\rho$ that was initialized earlier
than the current choice.

Unlike the first three cases, which correspond directly to~\gsetxt{} initialization rules, $\theta_\mathit{orig}$, case (iv), is unique to~\symtxt{}. In this case, $\theta_\mathit{orig}$ implements conditional initialization to preserve the original heap structure. This step is necessary in order to maintain \emph{homomorphism} (i.e., equivalent shapes) between symbolic heaps created using~\symtxt{} and the~\gsetxt{} heaps they are intended to represent. 
The sets from each of the four cases are added into the heap on $\cfgnt{r}_f$ after the fields
for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.

@@

\figref{fig:initHeap} illustrates the initialization process. The
graph in~\figref{fig:initHeap}(a) represents the initial heap. The
reference superscripts $s$ and $i$ indicate the partition containing
the reference: input, auxiliary, or stack.  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a
stack reference for the $\cfgt{this}$ variable which has two fields
$x$ and $y$ of the same type. Note that when no constraint is
specified for a location, there is an implicit $\mathit{true}$
constraint. For example, $\cfgnt{r}_0^s$ points to $\cfgnt{l}_0$ on
the constraint $\mathit{true}$. The fields $x$ and $y$ point to the
uninitialized reference $\cfgnt{r}_\mathit{un}$. The graph
in~\figref{fig:initHeap}(b) represents the symbolic heap after the
initialization of the $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$ field
while the graph in~\figref{fig:initHeap}(c) represents the symbolic
heap after the initialization of the
$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$ field following the
initialization of $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$. The list
in~\figref{fig:initHeap}(d) represents the various sets constructed in
the initialization for $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$.

@@

There are two rewrite rules in~\figref{fig:fHeap}, one for reading
the value of a field (field-access) and the other for writing to a
field (field-write). Both rules first check that the operations can be
performed on a non-null location. The field-access rewrite rule
in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$, recall that the heaps are type consistent and programs are type safe, and
uses the $\rsum^*$ relation from \figref{fig:symInit}, to get a new symbolic heap that is
initialized on the field $\cfgnt{f}$. The symbolic heap is further
modified to include a new stack reference pointing to the guarded value set
(possible values of the field) returned during the dereferencing; the
new stack reference is the return value from the $\mathbb{VS}$ operation.

@@

Strengthening in the field write creates a value set, \cfgnt{X},  that contains two
types of locations: those for the case where the write is feasible
(the first call in \cfgnt{X}), and those for the case where it is not (the second
call in \cfgnt{X}). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
will point to the guarded value set $\cfgnt{L}(\cfgnt{r})$.
Whereas, if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will
continue to point to the constraint location pair it currently
references.  As the references are immutable, the rule creates fresh
references for each $\cfgnt{r}_\mathit{cur}$ and points them to the
appropriate value sets.

@@

The rewrite rule to compare two references in the symbolic heap is
shown in~\figref{fig:eqs}. The equals references-true rewrite rule
returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
\emph{can be equal}. Intuitively, $\Phi_\alpha$ contains all
constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may point to
the same location in the symbolic heap. The second set, $\Phi_0$,
contains constraints under which the reference $\cfgnt{r}_0$ points to
corresponding locations such that the reference $\cfgnt{r}_1$
\emph{does not} point to those locations under any
constraint. Finally, the set, $\Phi_1$, contains constraints under
which $\cfgnt{r}_1$ points to corresponding locations and
$\cfgnt{r}_0$ \emph{does not} point to those locations under any
constraint. The three sets of constraints are used to create a new path condition $\phi_g^\prime$
as an update of the current path condition $\phi_g$.  The update is accomplished by first taking the disjunction of the
constraints in $\Phi_\alpha$ to indicate that if any of the
constraints are satisfiable, then references $\cfgnt{r}_0$ and
$\cfgnt{r}_1$ can be equal. This disjunction is then conjoined with $\phi_g$ to form $\phi_g^\prime$. Furthermore, the conjunctions of negations to the
constraints in $\Phi_0$ and $\Phi_1$ is conjoined with $\phi_g^\prime$. This indicates for locations
that are not common to the references, the negations of their
constraints are satisfiable. The rule does not complete (i.e., is not
feasible) if the new global constraint is not satisfied on any
aliasing assignment. In such a case, the $\cfgt{true}$ outcome is not
possible on any symbolic heap. Before the rewrite rule returns
$\cfgt{true}$, it verifies the satisfiability of the updated global heap
constraint. The reference-false is the logical dual of the rule.

### 2015-10-28 vmcai-2016-tex/bisimulation.tex
Redefined some equals instances.
Addressed reviewer concerns

The theorems in this section establish the soundness and
completeness of the symbolic heap approach with respect to Generalized
Symbolic Execution (\gsetxt{}). Intuitively, the theorems imply that any properties proven
with~\gsetxt{} can also be proved using the~\symtxt{}
algorithm. What follows is a brief description of the requisite terminology,
followed by the theorem statements. The proofs for the theorems, as well as
the complete set of semantic rules for~\gsetxt{} and~\symtxt{} can
be found in ~\cite{Hillery:2015}.

The theorems assert the existence of a
bisimulation between sets of states related by~\gsetxt{} ($p \rgse
p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
q^\prime$). The relations are on the universe of \emph{well-formed}
states $S$, which have the properties in \secref{sec:symheap} with the
constraint that the states are \emph{feasible}: successors exist
unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
for~\gsetxt{} (see~\cite{Hillery:2015}): $\rgse = \rgse^\mathit{A} \cup
\rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup
\rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access
after evaluating the expression for the base reference $\lp
\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$, \emph{W} is
a field write after evaluating the expression for the right operand
$\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x^Y$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x^Y P^\prime \defeq \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose a set $P$ contains a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in~\gsetxt{}: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

The functional equivalence between heaps in states $p$
and $q$ requires both a mapping to relate the two heaps and a
constraint on the feasibility of that mapping in the presence of a
path constraint from symbolic execution. Subscripts indicate state tuple
members as in $p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$.
\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism}, given the universe of field indices $\mathcal{F}$ and the universe of locations $\mathcal{L}$, is 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q \defeq
\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \exists \phi_\beta\ ( (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
 )) ) ) ) )
\end{array}
$$
\end{definition}
\begin{definition}
\label{def:hc}
The \textbf{homomorphism constraint} is
%\begin{align*}
\[
\mathbb{HC}(p \rightharpoonup_{h} q) \defeq
\bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
\]
%\end{align*}
\end{definition}
The notation $\cfgnt{L}_p^\rightarrow$ denotes the image of $\cfgnt{L}_p$. Functional equivalence asserts a common structure in the two heaps under certain
conditions. It is used to relate states in $p \rgse
p^\prime$ to states in $q \rsym q^\prime$.
\begin{definition}
\label{representation}
States $(p\ q)$ are in the \textbf{representation relation}, $p \sqsubset q$, if and only if, $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $p \rightharpoonup_{h} q$
such that $\mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) )$.
The represented relation is extended to sets of states $P$ and a single state $q$ as
$P \sqsubset q \defeq \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
\end{definition}
The statement $p \sqsubset q$ ensures that a functionally equivalent
heap to the one in $p$ is present, by the homomorphism, and valid, by
the heap constraint and path constraint, in $q$. As the states in $P$
are only differentiated by heaps and those states are only
differentiated from $q$ by both the heap and path constraint in $q$,
$P \sqsubset q$ implies that $q$ is representative of all the states
in $P$ up to the given point of execution expressed in $\phi_q$.
\begin{definition}
\label{bisimulation}
The \textbf{functional associated to bisimulation} applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( q \rsym q^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( P \rsgse P^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
If $\sqsubset$ is a bisimulation, then the greatest fixed point of $F_\sim(\sqsubset)$ is the bisimilarity relation denoted by $\sim$.
\end{definition}
Other than the use of a meta-relation, $\rsgse$, \defref{bisimulation} reasons over the typical forward and backward
simulation~\cite{Sangiorgi:2011}.

In the following lemma, $S$ is the universe of well-formed states, and $S_{FA} \subseteq S$ is the set of states at a field access continuation having computed the base reference.
\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisimulation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

@@

Similar lemmas are proved for field write and equals reference. These
require additional lemmas on the summarize machine
$\rightarrow_S$: that it preserves determinism, the
homomorphism, and the satisfiability of the homomorphism constraint

>>>>

The theorems in this section establish the soundness and
completeness of the symbolic heap approach with respect to \gsetxt{}. Intuitively, the theorems imply that any properties proven
with~\gsetxt{} can also be proven using the~\symtxt{}
algorithm. What follows is a brief description of the requisite terminology,
followed by the theorem statements. The proofs for the theorems, as well as
the complete set of semantic rules for~\gsetxt{} and~\symtxt{} are in ~\cite{Hillery:2015}.

The theorems assert the existence of a
bisimulation between sets of states related by~\gsetxt{} ($p \rgse
p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
q^\prime$). The relations are on the universe of \emph{well-formed}
states $S$, which have the properties in \secref{sec:symheap} with the
constraint that the states are \emph{feasible}: successors exist
unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
for~\gsetxt{}: $\rgse = \rgse^\mathit{A} \cup
\rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup
\rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access
after evaluating the expression for the base reference $\lp
\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$, \emph{W} is
a field write after evaluating the expression for the right operand
$\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x^Y$, is
extended to sets of states as
$$
P \hookrightarrow_x^Y P^\prime \defeq \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse \defeq \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose a set $P$ contains a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in~\gsetxt{}: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

The functional equivalence between heaps in states $p$
and $q$ requires both a mapping to relate the two heaps and a
constraint on the feasibility of that mapping in the presence of a
path constraint from symbolic execution. Subscripts indicate state tuple
members as in $p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$.
\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism}, given the universe of field indices $\mathcal{F}$ and the universe of locations $\mathcal{L}$, is 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q\ \defeq \ 
\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \exists \phi_\beta\ ( (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
 )) ) ) ) )
\end{array}
$$
\end{definition}
\begin{definition}
\label{def:hc}
The \textbf{homomorphism constraint} is
%\begin{align*}
\[
\mathbb{HC}(p \rightharpoonup_{h} q) \defeq
\bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
\]
%\end{align*}
\end{definition}
The notation $\cfgnt{L}_p^\rightarrow$ denotes the image of $\cfgnt{L}_p$. Functional equivalence asserts a common structure in the two heaps under certain
conditions. It is used to relate states in $p \rgse
p^\prime$ to states in $q \rsym q^\prime$.
\begin{definition}
\label{representation}
States $(p\ q)$ are in the \textbf{representation relation}, $p \sqsubset q$, if and only if, $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $p \rightharpoonup_{h} q$
such that $\mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) )$.
The represented relation is extended to sets of states $P$ and a single state $q$ as
$P \sqsubset q \defeq \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
\end{definition}
The statement $p \sqsubset q$ ensures that a functionally equivalent
heap to the one in $p$ is present, by the homomorphism, and valid, by
the heap constraint and path constraint, in $q$. As the states in $P$
are only differentiated by heaps and those states are only
differentiated from $q$ by both the heap and path constraint in $q$,
$P \sqsubset q$ implies that $q$ is representative of all the states
in $P$ up to the given point of execution expressed in $\phi_q$.
\begin{definition}
\label{bisimulation}
The \textbf{functional associated to bisimulation} applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( q \rsym q^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( P \rsgse P^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
\end{equation}
If $\sqsubset$ is a bisimulation, then the greatest fixed point of $F_\sim(\sqsubset)$ is the bisimilarity relation denoted by $\sim$.
\end{definition}
Other than the use of a meta-relation, $\rsgse$, \defref{bisimulation} reasons over the typical forward and backward
simulation~\cite{Sangiorgi:2011}.

In the following lemma, $S$ is the universe of well-formed states, and $S_{\mathit{FA}} \subseteq S$ is the set of states at a field access continuation having computed the base reference.
\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisimulation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

@@

Similar lemmas are proven for field write and equals reference. These
require additional lemmas on the initialization relation
$\rightarrow_S$: that it preserves determinism, the
homomorphism, and the satisfiability of the homomorphism constraint.

### 2015-10-28 vmcai-2016-tex/conclusion.tex
Addressed reviewer concerns

This work presents a
heap representation for symbolic execution that maintains exactness,
represents arbitrary heap structures without restrictions on aliasing
relationships, and supports dynamic on-the-fly initialization of heap
structures. This unique combination of capabilities enables the
symbolic heap algorithm to outperform state-of-the-art symbolic
execution techniques, and in some cases, the performance gains are
considerable. The performance gains in symbolic execution
may naturally benefit a variety of analyses based on symbolic
execution, for example, verification of properties, especially those
related to the heap, test case generation, program evolution
techniques such as directed incremental symbolic
execution~\cite{person:pldi2011}, and other back-end analyses. Potential future work includes evaluating the impact of analyses that rely on
symbolic execution.

>>>>

This paper presents a \symtxt{} algorithm for uninitialized
references in a fully symbolic heap. Where GSE lazily instantiates
uninitialized references to either NULL, a new instance of the correct
type, or an alias to a previously initialized object, the symbolic
initialization in this work creates a guarded value set expressing all
of these eventualities in the same symbolic heap. The paper includes a proof that the
\symtxt{} algorithm is sound and complete with respect to properties
provable by GSE.

An initial implementation of the technique has been done within the
Java PathFinder framework. The \symtxt{} algorithm outperforms
state-of-the-art case-splitting based symbolic execution techniques,
and in some cases, the performance gains are considerable in a set of
common Java data structure artifacts used to benchmark symbolic representations. The performance gains in symbolic
execution may naturally benefit a variety of analyses based on
symbolic execution, for example, verification of properties,
especially those related to the heap, test case generation, program
evolution techniques such as directed incremental symbolic
execution~\cite{person:pldi2011}, and other back-end
analyses. Potential future work includes evaluating the impact of
analyses that rely on symbolic execution and solving the problem of detecting heap entailment.
